Weakly Nonlinear MRI: Notes

### 2014-06-10 notes/mri_notes.tex
python code added
fixed typo
added coarse grid figure

@@

$\mathbf{V} = \mathbf{V}\left(x, z, Z, T)\right)$ where in detail $\mathbf{V} = \left[\Psi(x), u_{1y}(x), A(x), B_{1y}(x)\right]^T \alpha\left(Z, T\right) e^{st + ik_z z}$. Periodicity in $z$ allows us to posit the exponential $z$ dependence. \\

@@

@@

@@

$\frac{1}{\reym} \partial_x^2 A^\dagger \, - \, \frac{1}{4\pi} i A \partial_x^2 \Psi^\dagger \, + \, q i Q B^\dagger \, - \, Q^2 \frac{1}{\reym} A^\dagger \, + \, i Q^3 \frac{1}{4\pi} \Psi^\dagger \, = \, 0$ \\

@@

The above is coded up in \texttt{adjoint\_homogenous.py}.

>>>>

$\partial_t A \, = \, B_0 \partial_z \Psi \, + \, J\left(A, \Psi\right) \, + \, \frac{1}{\reym} \nabla^2 A$ \\

@@

$\mathbf{V} = \mathbf{V}\left(x, z, Z, T\right)$ where in detail $\mathbf{V} = \left[\Psi(x), u_{1y}(x), A(x), B_{1y}(x)\right]^T \alpha\left(Z, T\right) e^{st + ik_z z}$. Periodicity in $z$ allows us to posit the exponential $z$ dependence. \\

@@

\section*{Matrix Formulation}

@@

\section*{Solvability Conditions}

@@

$\frac{1}{\reym} \partial_x^2 A^\dagger \, - \, \frac{1}{4\pi} i Q \partial_x^2 \Psi^\dagger \, + \, q i Q B^\dagger \, - \, Q^2 \frac{1}{\reym} A^\dagger \, + \, i Q^3 \frac{1}{4\pi} \Psi^\dagger \, = \, 0$ \\

@@

The above is coded up in \texttt{adjoint\_homogenous.py}. \\

To determine what the critical values $\reym = \reym_{crit}$ and $k_z = Q$, we solve the linearized MRI equations for a number of $\reym$ and $k_z$ values to determine criticality. \\

We reproduce Fig. 1b of Umurhan+: \\

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{s_Re_Im_Co_coarse}
\caption{Real and Imaginary parts of parameter space for linear MRI system.}
\label{onoff}
\end{figure*}

By solving the linear MRI system on a coarse parameter space grid. \\
